Byzantine Fault-Tolerant and Locality-Aware Scheduling MapReduce

### 2019-08-26 sample-sigchi.tex
up

\item[Worker Process] A Worker Process executes map and reduce task

@@

>>>>

\item[Worker Process] A Worker Process executes map and reduce task scheduleted by current Leader Primary Process. In order to achieve fault tolerance, any Worker Process must be run indepently on different host. In our implementation, each process run on independent Amazon EC2 server

@@

\subsection{The algorithm}

In order to achieve 
A simplistic solution to make MapReduce
Byzantine fault-tolerant given the system model would be the
following. First, the JobTracker starts 2f + 1 replicas of each
map task in different servers and TaskTrackers. Second, the
JobTracker starts also 2f + 1 replicas of each reduce task.
Each reduce task fetches the output from all map replicas,
picks the most voted results, processes them and stores its
output in HDFS. In the end, either the client or a special task
must make the vote of the outputs to pick the most voted. An
even more simplistic solution would be to run a consensus,
or Byzantine agreement between each set of map task repli-
cas and reduce task replicas. This would involve even more
replicas (typically 3f + 1) and more messages exchanged.
